{\cis}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2018-11-04 papers/lang2018/ms.tex
Replace OSX in images and paper content to MacOS

%---------------------------------------------------------------------------------
% ABSTRACT (145 words)
\begin{abstract}
Thousands of computational models have been created within the plant biology community in the past two decades that have the potential to be combined into complex integration networks capable of capturing more complex biological processes than possible with isolated models. However, the technological barriers introduced by differences in language and data formats has slowed this progress. We present \href{https://github.com/cropsinsilico/cis_interface}{\cis}, a Python package for running integration networks with connections between models across languages and scales. {\cis} coordinates parallel execution of models in Python, C, C++, and Matlab on Linux, Mac OS X, and Windows operating systems, and handles communication in a number of data formats common to computational plant modeling. {\cis} is designed to be user-friendly and can be accessed at {\tt https://github.com/cropsinsilico/cis\_interface}.
\end{abstract}

>>>>

%---------------------------------------------------------------------------------
% ABSTRACT (145 words)
\begin{abstract}
Thousands of computational models have been created within the plant biology community in the past two decades that have the potential to be combined into complex integration networks capable of capturing more complex biological processes than possible with isolated models. However, the technological barriers introduced by differences in language and data formats has slowed this progress. We present \href{https://github.com/cropsinsilico/cis_interface}{\cis}, a Python package for running integration networks with connections between models across languages and scales. {\cis} coordinates parallel execution of models in Python, C, C++, and Matlab on Linux, Mac OS, and Windows operating systems, and handles communication in a number of data formats common to computational plant modeling. {\cis} is designed to be user-friendly and can be accessed at {\tt https://github.com/cropsinsilico/cis\_interface}.
\end{abstract}
